Time Series Length at Which Block Bootstrapping is Effective for Estimation of Variance

### 2022-10-27 Manuscript/manuscript.tex
Fix?
manuscript.tex

As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was 
required for effective block bootstrap estimation. The tables below for each corresponding block length function and AR Coefficient display information about the length of the sample of the ARIMA process, the block length used in bootstrap, the method (non-moving or moving), and the proportion of 95\% confidence intervals produced by each of 4000 block bootstrap replications that recover the mean, as well as an interval in which we can be 95\% confident that the true coverage rate given an infinite number of replications is contained. 
As shown in the plots, as n decreases, the coverage rate decreases. As AR increases, not only is a larger sample size required for effective bootstrap estimation, but the level of noise also increases. The best block length function, as shown in previous literature, is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20. For the larger sample sizes, there does not appear to be a significant difference in results for moving method vs non-moving method. However, block bootstrap with moving method appears to perform better for smaller sample sizes than block bootstrap with non-moving method.

@@

\bibliographystyle{chicago}
\bibliography{citations.bib}[tp]

>>>>

As the AR Coefficient increases, it was found unsurprisingly that a larger sample size was 
required for effective block bootstrap estimation. The tables below for each corresponding block length function and AR Coefficient display information about the length of the sample of the ARIMA process, the block length used in bootstrap, the method (non-moving or moving), and the proportion of 95\% confidence intervals produced by each of 4000 block bootstrap replications that recover the mean, as well as an interval in which we can be 95\% confident that the true coverage rate given an infinite number of replications is contained. 
As shown in the plots, as n decreases, the coverage rate decreases. As AR increases, not only is a larger sample size required for effective bootstrap estimation, but the level of noise also increases. The best block length function, as shown in previous literature, \citep{buhlmann1999block} is l = n$^{1/3}$, as it yields the most consistently high coverage rates even for samples as small as n = 20. l = 10 seems to perform better than l = $\sqrt{n}$ for higher sample sizes, but the coverage rates for l = 10 drop down much more for small sample sizes than l = $\sqrt{n}$. For the larger sample sizes, there does not appear to be a significant difference in results for moving method vs non-moving method. However, block bootstrap with moving method appears to perform better for smaller sample sizes than block bootstrap with non-moving method.

@@

\bibliographystyle{chicago}
\bibliography{citations}[tp]
